%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Pitch Perfect} $|$ \emph{Java, HTML/CSS, JSoup, JavaScript, NLP API, AJAX, JDBC, MySQL, Git}}{}
    \resumeItemListStart
        \resumeItem{Designed and programmed a responsive web application and database, that helps discover sport activities and book facilities nearby.}
        \resumeItem{The website makes use of third-party data (from web scraping and a web service), which is processed with a Servlet and accessed with AJAX. There is also SQL used for database creation and that is accessed via Servlets.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{SPFD} $|$ \emph{Python, Tkinter, Bash, RPi.GPIO, FreeCAD, Fritzing, Ultimaker Cura}}{}
    \resumeItemListStart
        \resumeItem{ Designed and implemented a DIY Smart Pet Food Dispenser using a Raspberry Pi, with a automated weighing system that controls the amount of food and delivery intervals while enabling customization.}
        \resumeItem{The entire food dispenser and housing model for the RPi was designed in FreeCAD after measuring individual components. Ultimaker Cura was used to slice the 3D-model to obtain the gcode file to 3D print.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Auto-Fill} $|$ \emph{Python, HTML/CSS, JavaScript, Selenium, PyQt, Git, Figma}}{}
    \resumeItemListStart
        \resumeItem{Designed and implemented a productivity application with a Graphical User Interface (GUI) that deals with Business Process Automation (BPA). It automates the process of manual data entry onto online submission forms.}
        \resumeItem{For scripting purposes Python and JavaScript was used. The User Interface was designed using PyQt (Python Plug-in). Selenium web framework was used for browser automation.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
